A holomorphic approach to membranes and fivebranes

### 2022-08-02 fivebranes/fact.tex
update

In this section we use the formalism of factorization algebras to give a conjectural description of observables of the universal membrane and fivebrane worldvolume theories (after twisting). 
Our ansatz relies on a proposal for twisted holography developed by \brian{cites}.

The observables of any theory in the BV formalism have the structure of a factorization algebra on spacetime \cite{CG2}. 
Classically, if a theory in the BV formalism is described by a local $L_\infty$ algebra $\cL$ on spacetime $M$ then to an open set $U \subset M$ the factorization algebra of observables assigns the cochain complex
\[
\clie^\bu(\cL(U))
\]
which computes the Lie algebra cohomology of $\cL(U)$. 
The differential on this cochain complex is precisely the Chevellay--Eilenberg differential associated to the~$L_\infty$ structure maps.

@@

We briefly highlight an analogous construction of the restricted factorization algebra which is natural from the point of view of membranes.
Recall that in the twist we are considering the worldvolume theory of membranes is a three-dimensional partially topological-holomorphic field theory which exist on a product $\R \times C$ where $C$ is a Riemann surface.

@@

As in the case of fivebranes, this proposition allows us to decompose the local Lie algebra $\cG_{\R \times C}$ into weights. 
Similarly to the proof of Lemma \ref{lem:technical} one can show that the $n$th eigenspace is quasi-isomorphic to a local Lie algebra of the form
\[
\Omega^\bu(\R) \otimes \Omega^{0,\bu}\left(C, \cV^{(n)}\right)
\]
where $\cV^{(n)}$ is a holomorphic super vector bundle on $C$.

We will state explicit descriptions of the first few eigenspaces without details of the proof. 
The first nontrivial eigenspace is, as in the fivebrane case, $n=-1$. 
Here, one can see that 
\[
\cV^{(-1)} \simeq K_{C}^{1/4} \otimes \C^4 \oplus \Pi K^{3/4}_C \otimes \C^4 .
\]
For $n=0$ one has 
\[
\cV^{(0)} \simeq \T_C \oplus \lie{sl}(4) \otimes \cO_C \oplus \Pi \left(K^{-1/2}_C \otimes \wedge^2 \C^4 \oplus K^{-1/2}_C \otimes S^2 \C^4\right) .
\]

@@

In quantum field theory Koszul duality naturally appears in the problem of coupling topological line operators to some ambient bulk theory. 
More generally, for higher dimensional topological defects, this problem is encoded by Koszul duality for the theory of $\EE_n$ algebras \cite{??}.

@@

In this first part of this subsection we briefly recall how Koszul duality enters in the problem of coupling line operators. 
We refer~\cite[\S 6]{CP1},~\cite[\S ??]{CG1}, or the review~\cite{PWkoszul} for more details. 
Then, we give an ansatz for Koszul duality for factorization algebras of the form $\clie^\bu(\cL)$ where $\cL$ is some local Lie algebra. 
From the point of view of the BV formalism this is not much of a condition, all such factorization algebras of classical observables can be cast in this form.

@@

\begin{prop}
Let $\lie{g}$ be a Lie algebra and equip the associative (and commutative) dg algebra $\clie^\bu(\fg)$ with the augmentation induced by the tautological homomorphism $0 \to \lie{g}$.
The Koszul dual of $\clie^\bu(\lie{g})$ with respect to this augmentation is equivalent to the universal enveloping algebra $U \fg$. 
\end{prop}

@@

Similarly, a model for $U \fg$ is the locally constant factorization algebra
\[
\clie_\bu(\fg \otimes \Omega^\bu_{\R,c}).
\]
To an open set $U \subset \R$ this produces the Chevellay--Eilenberg complex computing the Lie algebra {\em homology} of the dg Lie algebra $\fg \otimes \Omega^\bu_c(U)$---the $\fg$-valued compactly supported de Rham forms on $U$.

@@

While we don't prove that the factorization algebra $\clie^\bu(\cL)^!$ satisfies any sort of categorical duality, we point out a universality that is satisfied with reference to couplings.
In \cite[Chapter ??]{CG2} a factorization algebra enhancement of Noether's theorem is formulated. 
The general context is the following: 
\begin{itemize}
\item $\cB$ is the factorization algebra on spacetime $M$ of classical observables for some auxiliary theory in the BV formalism.
\item $\cL$ is a local Lie algebra on $M$ which acts on the theory by local symmetries. 
\end{itemize}
Then, the classical version of Noether's theorem for factorization algebras produces a map of factorization algebras 
\[
\clie_\bu(\cL_c) \to \cB .
\]

@@

The limit diagram \eqref{eqn:lim} induces a diagram of factorization algebras
\beqn\label{eqn:colim}
\ul\C \to \clie^\bu(\cG_1) \to \clie^\bu(\til \cG_2) \to \cdots ,
\eeqn
whose colimit is~$\Bar{\pi}_* \Obs_{sugra}$. 
Here $\ul\C$ is the constant factorization algebra whose value is $\C$ on every open set. 
Applying~$!$-duals we obtain a sequence
\beqn
\ul\C \leftarrow \clie_\bu(\cG_{1,c}) \leftarrow \clie_\bu (\til \cG_{2,c}) \leftarrow \cdots ,
\eeqn 
whose limit is $\clie_\bu(\cG_c) = (\Bar{\pi}_* \Obs_{sugra})^!$. 
We also point out that there is a similar diagram of the form
\beqn
\clie_\bu (\cG_{2,c}) \leftarrow \clie_\bu (\cG_{2,c}) \leftarrow \cdots .
\eeqn

\end{document}

>>>>

In this section we use the formalism of factorization algebras to give a conjectural description of observables of the universal membrane and fivebrane worldvolume theories (after twisting).
For the case at hand, our expectation for universal can be understood as the theory on a large number of membranes and fivebranes. 
We will see how this interpretation is supported by the supergravity index calculations presented in the last section.

Our ansatz for the worldvolume theories in the large $N$ limit relies on a proposal for twisted holography proposed by Costello and Li in \cite{CLsugra} and further developed by Costello, Gaiotto, Paquette in \cite{CostelloM2,CostelloOmega,costello2021twisted,CP}.
The core idea is that the algebra of operators on both sides of the duality are Koszul dual. 
Many other examples and support for this twisted holographic principle have been carried out in \cite{Oh:2021wes,Oh:2020hph,Gaiotto:2021xce}. \brian{surya add more?}

It is absolutely crucial for this proposal that we work in a derived setting using the BV formalism. 
The observables of any theory in the BV formalism have the structure of a factorization algebra on spacetime \cite{CG2}. 
Classically, if a theory in the BV formalism is described by a local $L_\infty$ algebra $\cL$ on spacetime $M$ then to an open set $U \subset M$ the factorization algebra of observables assigns the cochain complex
\[
\clie^\bu(\cL(U))
\]
which computes the Lie algebra cohomology of $\cL(U)$. 
The differential on this cochain complex is precisely the Chevellay--Eilenberg differential associated to the~$L_\infty$ structure maps.

@@

We briefly highlight an analogous construction of the restricted factorization algebra describing membranes.
Recall that in the twist we are considering the worldvolume theory of membranes is a three-dimensional partially topological-holomorphic field theory which exist on a product $\R \times C$ where $C$ is a Riemann surface.

@@

As in the case of fivebranes, this proposition allows us to decompose the local Lie algebra $\cG_{\R \times C}$ into weights. 
Similarly as above one can show that the $n$th eigenspace is quasi-isomorphic to a local Lie algebra of the form
\[
\Omega^\bu(\R) \otimes \Omega^{0,\bu}\left(C, \cV^{(n)}\right)
\]
where $\cV^{(n)}$ is a holomorphic super vector bundle on $C$.

We will state explicit descriptions of the first few eigenspaces without details of the proof. 
The first nontrivial eigenspace is, as in the fivebrane case, $n=-1$. 
Here, one can see that 
\[
\cV^{(-1)} \simeq K_{C}^{1/4} \otimes \C^4 \oplus \Pi K^{3/4}_C \otimes \C^4 .
\]
For $n=0$ one has 
\[
\cV^{(0)} \simeq \T_C \oplus \lie{sl}(4) \otimes \cO_C \oplus \Pi \left(K^{-1/2}_C \otimes \wedge^2 \C^4 \oplus K^{-1/2}_C \otimes S^2 \C^4\right) .
\]
As in the case of fivebranes, the $n=0$ eigenspace is equipped with the structure of a super Lie algebra whose exact form we do not state now.

@@

In quantum field theory Koszul duality naturally appears in the problem of coupling topological line operators to some ambient bulk theory. 
More generally, for higher dimensional topological defects, this problem is encoded by Koszul duality for the theory of $\EE_n$ algebras \cite{FrancisGaitsgory} \cite[\S 5.2]{LurieHA}.

@@

In this first part of this subsection we briefly recall how Koszul duality enters in the problem of coupling line operators. 
We refer~\cite[\S 6]{CP1},~\cite[\S 8]{CG1}, or the review~\cite{PWkoszul} for more details. 
Then, we give an ansatz for Koszul duality for factorization algebras of the form $\clie^\bu(\cL)$ where $\cL$ is some local Lie algebra. 
From the point of view of the perturbative BV formalism this is not much of a restriction, all such factorization algebras of classical observables can be cast in this form.

@@

\begin{prop}
Let $\lie{g}$ be a Lie algebra and equip the filtered associative (and commutative) dg algebra $\clie^\bu(\fg)$ with the augmentation induced by the tautological homomorphism $0 \to \lie{g}$.
The Koszul dual of $\clie^\bu(\lie{g})$ with respect to this augmentation is equivalent to the universal enveloping algebra $U \fg$. 
\end{prop}

@@

Similarly, a model for $U \fg$ is the locally constant factorization algebra
\[
\clie_\bu(\fg \otimes \Omega^\bu_{\R,c}),
\]
see \cite[\S 3.4]{CG1}.
To an open set $U \subset \R$ this produces the Chevellay--Eilenberg complex computing the Lie algebra {\em homology} of the dg Lie algebra $\fg \otimes \Omega^\bu_c(U)$---the $\fg$-valued compactly supported de Rham forms on $U$.

@@

While we don't prove that the factorization algebra $\clie^\bu(\cL)^!$ satisfies any sort of categorical duality, we point out a universality that is satisfied with reference to couplings.
In \cite[Part 3]{CG2} a factorization algebra enhancement of Noether's theorem is formulated. 
The general context is the following: 
\begin{itemize}
\item $\cB$ is the factorization algebra on spacetime $M$ of classical observables for some auxiliary theory in the BV formalism.
\item $\cL$ is a local Lie algebra on $M$ which acts on the theory by local symmetries. 
\end{itemize}
Then, the classical version of Noether's theorem for factorization algebras produces a map of factorization algebras 
\[
\clie_\bu(\cL_c) \to \cB .
\]

@@

The limit diagram \eqref{eqn:lim} induces a diagram of factorization algebras
\beqn\label{eqn:colim}
\ul\C \to \clie^\bu(\cG_1) \to \clie^\bu(\til \cG_2) \to \cdots ,
\eeqn
whose colimit is~$\Bar{\pi}_* \Obs_{sugra}$. 
Here $\ul\C$ is the constant factorization algebra whose value is $\C$ on every open set. 
Applying~$!$-duals we obtain a sequence
\beqn
\ul\C \leftarrow \clie_\bu(\cG_{1,c}) \leftarrow \clie_\bu (\til \cG_{2,c}) \leftarrow \cdots ,
\eeqn 
whose limit is $\clie_\bu(\cG_c) = (\Bar{\pi}_* \Obs_{sugra})^!$. 
We also point out that there is a similar diagram of the form
\beqn\label{eqn:limit2}
\clie_\bu (\cG_{2,c}) \leftarrow \clie_\bu (\cG_{2,c}) \leftarrow \cdots .
\eeqn

%\end{document}

### 2022-08-02 fivebranes/index.tex
update

\section{Twisted supergravity states}

The first entry of the AdS/CFT dictionary in traditional treatments is a matching between \textit{supergravity states} and local operators in the CFT \cite{}. The goal of this section is to provide constructions of spaces of supergravity states in our eleven-dimensional model, via geometric quantization. The state spaces on ${\rm AdS}_{7}\times S^{4}$ and ${\rm AdS}_{4}\times S^{7}$ have a remarkable property - they are naturally modules for certain infinite dimensional exceptional lie superalgebras. We conclude the section by computing characters for these modules and comparing them with large $N$ indices for fivebranes and membranes in the literature.

@@

\subsection{Twisted Backreactions}
We begin by describing the relevant backgrounds. In eleven-dimensional supergravity, the ${\rm AdS}_7 \times S^4$ and ${\rm AdS}_{4}\times S^{7}$ backgrounds are obtained by backreacting a number of fivebranes and membranes respectively in flat space \cite{Maldacena:1997re,WittenAdS}.
In \cite{RSW} we gave descriptions of twisted versions of these backgrounds. We will recall this construction, adapted to a slightly more global situation than is considered in \cite{RSW}.

@@

We consider the theory on $X = Tot (\R\oplus K_{C})$, with some number of twisted `fivebranes' wrapping the zero section
\[
0 \times C \subset \R \times \T^* C .
\]
Denote by $t$ the real coordinate and by $w$ the fiber coordinate in $\T^* C$. We wish to describe the complement of the zero section $M = X - 0 \times C$.

Note that the bundle $\R\oplus K_{C}$ is equipped with a partially flat connection - this data equips the total space $X$ with the data of a transversely holomorphic foliation (THF).

@@

The reason that the boundary modifications take this form can be seen by understanding in more explicit terms the vacuum boundary condition.
The phase space at the boundary $C$ can be identified with the following cohomology
\[
\Omega^{0,\bu}(C) \otimes \cA^{0;\bu}(\R \times \C - 0) [1]
\]
where $\cA^{0;\bu}$ denotes the mixed de Rham--Dolbeault cohomology of $\R \times \C - 0$ as a manifold equipped with a transversely holomorphic foliation.
We refer to the section below for a reminder on this geometric structure.

@@

\subsection{Global symmetry for twisted fivebranes}
\label{s:global1}

After complexification, the~six-dimensional superconformal algebra is $\lie{osp}(8|4)$ whose even part is $\lie{so}(8) \times \lie{sp}(4)$. 
This algebra contains the six-dimensional $\cN=(2,0)$ supersymmetry algebra whose odd part is four copies of $S_+$, the positive irreducible complex spin representation of $\lie{so}(6)$.
The holomorphic supercharge is a supertranslation 
\[
Q \in \Pi S_+ \otimes \C^4 \subset \lie{osp}(8|4)
\]
which is characterized (up to equivalence) by the properties that $Q^2 = 0$ and that its image
\[
{\rm Im}\left(Q|_{\Pi S_+ \otimes \C^4} \right) \subset \R^6 \otimes_\R \C \cong \C^6
\]
is three-dimensional (spanned by the anti-holomorphic translations). 
The supercharge $Q$ acts on $\lie{osp}(8|4)$ by commutator and the resulting cohomology will automatically act on the holomorphic twist of any six-dimensional superconformal field theory. 
This cohomology can readily be identified with the subalgebra $\lie{osp}(6|2)$, see \cite{SWe36}.

In the untwisted situation, the symmetry of solutions to eleven-dimensional supergravity in the presence of fivebranes wrapping a six-dimensional affine subspace is exactly the superconformal algebra $\lie{osp}(8|4)$ (after complexification). 
Geometrically, this background is $AdS_7 \times S^4$. 
In \cite{RSW} we have proposed a twisted analog of the AdS background and have shown that solutions to equations of motion of our eleven-dimensional theory in the presence of twisted fivebranes contains the symmetry algebra $\lie{osp}(6|2)$---which is precisely the twisted superconformal algebra.

In this section we will compute characters of the single-particle gravitational states in our eleven-dimensional model for the geometry resulting from backreacting twisted fivebranes.
Such states have a symmetry by the twisted superconformal algebra $\lie{osp}(6|2)$. 
We will enumerate states via considering a Cartan in the even subalgebra
\beqn\label{eqn:bosonic1}
\lie{sl}(3) \times \lie{sl}(2) \times \lie{gl}(1) \subset \lie{osp}(6|2) .
\eeqn
%We will understand how the twisted superconformal algebra acts on fivebranes via holographic principles.

We recall how the bosonic subalgebra \eqref{eqn:bosonic1} of this twisted superconformal algebra embeds as symmetries of the eleven-dimensional theory in this twisted background. 
This manifests as an embedding of this bosonic subalgebra into the ghosts of the eleven-dimensional theory.

@@

\begin{rmk}
In the classification of simple super Lie algebras, Kac makes use of a weight grading $\oplus_{j \geq -2} \fg_j$ of $E(3|6)$ for which the finite-dimensional subalgebra above is the weight zero piece
\cite{KacClass}.
\end{rmk}

The dimension of a Cartan subalgebra is four and accordingly, the equivariant character we study has four fugacities.
We choose these explicitly as follows:
\begin{itemize}
  \item $t_{1}, t_{2}$ denote generators for the Cartan of $\lie{sl}(3)$ which is generated by the vector fields
  \beqn
  h_1 = z_1 \del_{z_1} - z_2 \del_{z_2} , \quad h_2 = z_2 \del_{z_2} - z_3 \del_{z_3}.
  \eeqn
   \item $q$ denotes a generator for the Cartan of the~$\lie{gl}(1)$ which is generated by the element~$\eqref{eqn:Y}$. 
  \item $r$ denotes a generator for the Cartan of a $\lie{sl}(2)$ which is generated by the element 
  \beqn
  h = \frac12 \left(w_1 \frac{\del}{\del w_1} - w_2 \frac{\del}{\del w_2}\right) .
  \eeqn
\end{itemize}
The weights are summarized in table \ref{tbl:weights1}.
Recall that the coordinates $(r_1,r_2)$ are used to label the basis of $\C^2$ in the space of fields $\Gamma^{hol}(\Hat{D}^3, K^{1/2}) \otimes \C^2$.

@@

\subsection{Global symmetry for twisted membranes}

\subsection{Counting supergravity states}

We enumerate single particle supergravity states via computing the super trace of the operator $t_1^{h_1} t_2^{h_2} q^Y r^h$. 
The super trace means that there is an extra factor of $(-1)^F$, where $F$ is parity (fermion number), when computing the ordinary trace.

\parsec[s:pexp]

\brian{characters, plethystic, etc.}

%\parsec[s:singleops]
%
%\begin{prop}
%Let $\Obs_{fivebrane}$ be the observables of the theory on a single fivebrane on $\C^3$ after performing the holomorphic twist.
%There is a quasi-isomorphism of super commutative dg algebras 
%\[
%\Obs_{fivebrane} (0) \simeq \Sym \left( I(0,0;1;-1)^* \right) .
%\]
%\end{prop}
%\begin{proof}
%This follows from Lemma \ref{lem:localops}.
%In \cite{SWsuca6d} a dg lift of Kac's module $I(0,0;1;-1)$ was defined with the following bigraded pieces:
%\beqn
%\text{bidegree} (-1,+)\colon \quad \Hat{\Omega}_3^{2} , \qquad \text{bidegree} (0,+)\colon \quad \Hat{\Omega}^{3}_3
%\eeqn
%and
%\beqn
%\text{bidegree} (-1, -)\colon \quad \Hat{\Omega}^{3/2}_{3} \otimes R .
%\eeqn
%The differential is the (algebraic) de Rham differential $\del \colon \Hat{\Omega}^2 \to \Hat{\Omega}^3$. 
%The differential is zero on the odd summand.
%We will call this cochain complex $(E_{fivebrane}(\Hat{D}^3), \del)$.
%
%From the description of the fields of the holomorphic twist of the single fivebrane it is easy to see that the Taylor expansion at $0 \in \C^3$ defines a cochain map
%\[
%(\cE_{fivebrane} (\C^3), Q) \to (E_{fivebrane}(\Hat{D}^3), \del) 
%\]
%That this induces a quasi-isomorphism $J_0^\infty \cE_{fivebrane} \simeq E (\Hat{D}^3)$ follows from the Dolbeault Poincar\'e lemma.
%\end{proof}

\subsection{The large $N$ limit}

We now compute the equivariant character counting local operators of the holomorphic twist of the theory on a large number of fivebranes. 
Unlike the analysis above, we will the twisted holography proposal to compute this character. We consider the equivariant character of local operators of the holomorphic twist of a large number of fivebranes with respect to a finite dimensional subalgebra
\[
\lie{sl}(3)\times \lie{sl}(2)\times \lie {gl}(1)\subset E(5|10)
\]
which embeds in the following way:
\begin{itemize}
\item The Lie algebra $\lie{sl}(3)$ is a subalgebra of $\Vect_0(\Hat{D}^3) \subset \Vect_0 (\Hat{D}^5)$ consisting of linear coefficient vector fields $\sum_{i,j} a_{ij} z_i \frac{\del}{\del z_j}.$
where $(a_{ij}) \in \lie{sl}(3)$. 
\item The Lie algebra $\lie{sl}(2)$ rotates the directions $\C_{w_1} \times \C_{w_2}$ transverse to the brane.
\item The one-dimensional Lie algebra $\lie{gl}(1)$ is spanned by the vector field 
\beqn\label{vf1}
\sum_i z_i \frac{\del}{\del z_i} - \frac23 \sum_{j} w_j \frac{\del}{\del w_j} \in \Vect_0(\Hat{D}^5).
\eeqn
\end{itemize}

Correspondingly, the equivariant character thus has four fugacities, which we label as follows:
\begin{itemize}
  \item $t_{1}, t_{2}$ again denote generators for the Cartan of $\lie{sl}(3)$ acting by vector fields on $\C^{3}_{z}$.
  \item $r$ denotes a generators for the Cartan of a $\lie{sl}(2)$ acting by the fundamental representation on the normal directions $\C_{w_1} \times \C_{w_2}$.
  \item $q$ denotes a generator for the Cartan of additional $\lie{gl}(1)$ generated by the divergence-free vector field \eqref{vf1}. 
\end{itemize}

This choice of weights is summarized in Table \ref{tbl:sugra}.

\begin{table}
\begin{center}
\begin{tabular}{c c c c c c}
  & $z_{1}$ & $z_{2}$ & $z_{3}$ & $w_{1}$ & $w_{2}$ \\
  \hline
  $t_{1}$ & $1$ & 0 & $-1$ & 0 & 0 \\
  $t_{2}$ & 0 & 1 & $-1$ & 0 & 0 \\
  $r$ & 0 & 0 & 0 & 1 & $-1$ \\
  $q$ & $-1$ & $-1$ & $-1$ & $\frac{3}{2}$ & $\frac{3}{2}$
\end{tabular}
\caption{Fugacities for the fields of the holomorphic twist of eleven-dimensional supergravity.}
\label{tbl:sugra}
\end{center}
\end{table}

\begin{prop}
  The character of local operators of the holomorphic twist of the theory on a large number of fivebranes is given by the following plethystic exponential

  \[ \rm PExp [f_{large N}(t_{1}, t_{2}, q, r)] \]

  where the single particle index is \[f_{large N}(t_{1}, t_{2}, q, r) = \frac{q^4(t_1^{-1}+t_1t_2^{-1}+t_2)-q^2(t_1+t_1^{-1}t_2+t_2^{-1})+(q^{3/2}-q^{9/2})(r+r^{-1})}{(1-t_{1}^{-1}q)(1-t_{2}q)(1-t_{1}t_{2}^{-1}q)(1-rq^{3/2})(1-r^{-1}q^{3/2})}.\]
\end{prop}

The specialization $t_1=t_2=r=1$ yields the single particle index
\[
\frac{3 q^4 - 3 q^2 + 2 q^{3/2} - 2 q^{9/2}}{(1-q)^3 (1-q^{3/2})^2} .
\]

\parsec 
The specialization of this index $q=r^2, t_2=1$ in \eqref{eqn:special1} yields the plethystic exponential of the following single particle index
\[
f_{two}(t_1, 1, q, q^{1/2}) = \frac{q}{(1-q)^2}
\]

\parsec The same change of variables in \eqref{eqn:special2} agrees with previously computed indices for single particle states for supergravity on $AdS_{7}\times S^{4}$ \surya{...}

>>>>

\section{Twisted supergravity states}
\label{sec:states}

The first entry of the AdS/CFT dictionary in traditional treatments is a matching between \textit{supergravity states} and local operators in the CFT. 
The goal of this section is to provide constructions of spaces of twisted supergravity states in our eleven-dimensional model, via geometric quantization. The state spaces on ${\rm AdS}_{7}\times S^{4}$ and ${\rm AdS}_{4}\times S^{7}$ have a remarkable property---they are naturally modules for certain infinite-dimensional exceptional super Lie algebras. We conclude the section by computing characters for these modules and comparing them with large $N$ indices for fivebranes and membranes in the literature.

@@

\subsection{Twisted Backreactions}
We begin by describing the relevant backgrounds. In eleven-dimensional supergravity, the $AdS_7 \times S^4$ and $AdS_{4}\times S^{7}$ backgrounds are obtained by backreacting a number of fivebranes and membranes respectively in flat space \cite{Maldacena:1997re,WittenAdS}.
In \cite{RSW} we gave descriptions of twisted versions of these backgrounds. We will recall this construction, adapted to a slightly more global situation than is considered in \cite{RSW}.

@@

We consider the theory on $X = \text{Tot} (\R\oplus K_{C})$, with some number of twisted `fivebranes' wrapping the zero section
\[
0 \times C \subset \R \times \T^* C .
\]
Denote by $t$ the real coordinate and by $w$ the fiber coordinate in $\T^* C$. We wish to describe the complement of the zero section $M = X - 0 \times C$.

Note that the bundle $\R\oplus K_{C}$ is equipped with a partially flat connection - this data equips the total space $X$ with the data of a transversely holomorphic foliation (THF) \cite{DuchampKalka}.

@@

The reason that the boundary modifications take this form can be seen by understanding in more explicit terms the vacuum boundary condition.
The phase space at the boundary $C$ can be identified with the following cohomology
\[
\Omega^{0,\bu}(C) \otimes \cA^{0;\bu}(\R \times \C - 0) [1]
\]
where $\cA^{0;\bu}$ denotes the mixed de Rham--Dolbeault cohomology of $\R \times \C - 0$ as a manifold equipped with a transversely holomorphic foliation \cite{DuchampKalka}.
We refer to the section below for a reminder on this geometric structure.

@@

\subsection{Global symmetry for twisted $AdS$}
\label{s:global1}

After complexification, the~six-dimensional and three-dimensional superconformal algebras are isomorphic to $\lie{osp}(8|4)$.
The even part of this algebra is $\lie{so}(8) \times \lie{sp}(4)$.
This algebra contains the six-dimensional $\cN=(2,0)$ supersymmetry algebra whose odd part is four copies of $S^{6d}_+$, the positive irreducible complex spin representation of $\lie{so}(6)$.
It also contains the three-dimensional $\cN=8$ supersymmetry algebra whose odd part is eight copies of $S^{3d}$, the irreducible complex spin representation of $\lie{so}(3)$.

In the six-dimensional case, the holomorphic supercharge is a supertranslation 
\[
Q \in \Pi S^{6d}_+ \otimes \C^4 \subset \lie{osp}(8|4)
\]
which is characterized (up to equivalence) by the properties that $Q^2 = 0$ and that its image
\[
{\rm Im}\left(Q|_{\Pi S_+ \otimes \C^4} \right) \subset \R^6 \otimes_\R \C \cong \C^6
\]
is three-dimensional (spanned by the anti-holomorphic translations). 
The supercharge $Q$ acts on $\lie{osp}(8|4)$ by commutator and the resulting cohomology will automatically act on the holomorphic twist of any six-dimensional superconformal field theory. 
This cohomology can readily be identified with the subalgebra $\lie{osp}(6|2)$, see \cite{SWe36}.

Similarly, the minimal twisting supercharge in the three-dimensional $\cN=8$ supersymmetry algebra is an element $Q \in \Pi S^{3d} \otimes \C^8$ which is characterized (up to equivalence) by the property that $Q^2 = 0$ and that the image of $[Q,-]$ is two-dimensional. 
The cohomology of $\lie{osp}(8|4)$ with respect to this supercharge is also isomorphic to~$\lie{osp}(6|2)$.

In the untwisted situation, the symmetry of solutions to eleven-dimensional supergravity in the presence of fivebranes wrapping a six-dimensional affine subspace is exactly the superconformal algebra $\lie{osp}(8|4)$ (after complexification). 
Geometrically, this background is $AdS_7 \times S^4$. 
Similarly, for backreacting membranes the background is $AdS_4 \times S^7$. 
In \cite{RSW} we have proposed a twisted analog of the $AdS$ background and have shown that solutions to equations of motion of our eleven-dimensional theory in the presence of twisted fivebranes and membranes contains the symmetry algebra $\lie{osp}(6|2)$---which is precisely the twists of the superconformal algebras we just discussed.

We will count the single-particle gravitational states in our eleven-dimensional model for the geometry resulting from backreacting twisted fivebranes and membranes.
Such states have a symmetry by the twisted superconformal algebra $\lie{osp}(6|2)$. 
We will enumerate states via choosing a Cartan in the following subalgebra of the twisted superconformal algebra
\beqn\label{eqn:bosonic1}
\lie{sl}(3) \times \lie{sl}(2) \times \lie{gl}(1) \subset \lie{osp}(6|2) .
\eeqn
%We will understand how the twisted superconformal algebra acts on fivebranes via holographic principles.

We will first recall how the bosonic subalgebra \eqref{eqn:bosonic1} of this twisted superconformal algebra embeds as symmetries of the eleven-dimensional theory in this twisted background. 
This manifests as an embedding of this bosonic subalgebra into the ghosts of the eleven-dimensional theory. 
The embedding is distinct for fivebranes and membranes.
We turn first to the fivebrane case.

\subsection{Supergravity states for twisted $AdS_7$}

@@

%\begin{rmk}
%In the classification of simple super Lie algebras, Kac makes use of a weight grading $\oplus_{j \geq -2} \fg_j$ of the exceptional Lie algebra $E(3|6)$ for which the finite-dimensional subalgebra above is the weight zero piece
%\cite{KacClass}.
%We will make use of this grading in \S \ref{s:kr}.
%\end{rmk}

The dimension of a Cartan subalgebra of $\lie{sl}(3) \times \lie{sl}(2) \times \lie{gl}(1)$ is four and accordingly, the equivariant character we study has four fugacities.
We choose these explicitly as follows:
\begin{itemize}
  \item $t_{1}, t_{2}$ denote generators for the Cartan of $\lie{sl}(3)$ which is generated by the vector fields
  \beqn
  h_1 = z_1 \frac{\del}{\del {z_1}} - z_2 \frac{\del}{\del{z_2}} , \quad h_2 = z_2 \frac{\del}{\del{z_2}} - z_3 \frac{\del}{\del{z_3}}.
  \eeqn
   \item $q$ denotes a generator for the Cartan of the~$\lie{gl}(1)$ which is generated by the element $Y$ from equation~$\eqref{eqn:Y}$. 
  \item $r$ denotes a generator for the Cartan of a $\lie{sl}(2)$ which is generated by the element 
  \beqn
  h = \frac12 \left(w_1 \frac{\del}{\del w_1} - w_2 \frac{\del}{\del w_2}\right) .
  \eeqn
\end{itemize}

The twisted supergravity states $\cH_{sugra}^{6d}$ form a representation for $\lie{osp}(6|2)$. 
The weights of twisted supergravity states with respect to the generators of the Cartan subalgebra above are completely determined by the weights of the holomorphic coordinates on $\C^2_w \times \C^3_z$.
These are summarized in table \ref{tbl:sugraM5}.

\begin{table}
\begin{center}
\begin{tabular}{c c c c c c}
  & $z_{1}$ & $z_{2}$ & $z_{3}$ & $w_{1}$ & $w_{2}$ \\
  \hline
  $t_{1}$ & $1$ & 0 & $-1$ & 0 & 0 \\
  $t_{2}$ & 0 & 1 & $-1$ & 0 & 0 \\
  $r$ & 0 & 0 & 0 & 1 & $-1$ \\
  $q$ & $-1$ & $-1$ & $-1$ & $\frac{3}{2}$ & $\frac{3}{2}$
\end{tabular}
\caption{Fugacities for the fields of the holomorphic twist of eleven-dimensional supergravity for the geometry $\R \times \C^5 \setminus \C^3$.}
\label{tbl:sugraM5}
\end{center}
\end{table}

We enumerate single particle supergravity states via computing the super trace of the operator $q^Y t_1^{h_1} t_2^{h_2} r^h$ acting on $\cH^{6d}_{sugra}$:
\beqn
f^{6d}_{sugra}(q,t_1,t_2,r) = \Tr_{\cH_{sugra}^{6d}} (-1)^F q^Y t_1^{h_1} t_2^{h_2} r^h .
\eeqn
The super trace means that there is an extra factor of $(-1)^F$, where $F$ is parity (fermion number), when computing the ordinary trace. 
That is, we compute the expression

\begin{prop}
The single particle index of the space of twisted supergravity states $\cH_{sugra}^{6d}$ is given by the following expression
\beqn
f_{sugra}^{6d} (q, t_{1}, t_{2}, r) = \frac{q^4(t_1^{-1}+t_1t_2^{-1}+t_2)-q^2(t_1+t_1^{-1}t_2+t_2^{-1})+(q^{3/2}-q^{9/2})(r+r^{-1})}{(1-t_{1}^{-1}q)(1-t_{2}q)(1-t_{1}t_{2}^{-1}q)(1-rq^{3/2})(1-r^{-1}q^{3/2})}.
\eeqn
\end{prop}

We record a few specializations of this index which we will remark on further in \S \ref{s:??}.
\parsec 
The specialization of this index $q=r^2, t_2=1$ in \eqref{eqn:special1} yields the plethystic exponential of the following single particle index
\[
f_{sugra}^{6d}(q, t_1, t_2=1, r = q^{1/2}) = \frac{q}{(1-q)^2}
\]

The specialization $t_1=t_2=r=1$ yields the single particle index
\[
f_{sugra}^{6d} (q, t_1=t_2=r=1) = \frac{3 q^4 - 3 q^2 + 2 q^{3/2} - 2 q^{9/2}}{(1-q)^3 (1-q^{3/2})^2} .
\]

\parsec The same change of variables in \eqref{eqn:special2} agrees with previously computed indices for single particle states for supergravity on $AdS_{7}\times S^{4}$ \surya{...} \brian{not sure where this was supposed to go?}

\subsection{Supergravity states for twisted $AdS_4$}

@@
